---
title: "Analysis Of Fund zhao "
author: "Wu Wei"
date: "2017-9-7"
output: html_document
---


## 1. Library input & Data Input
```{r library, echo = FALSE}
rm(list = ls())

suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(lmtest))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))
suppressMessages(library(Rdonlp2))
suppressMessages(library("FinTS"))
```

```{r source, echo = FALSE}
source("d://MyR//stock//CompareObjectNaiveAccuracy.R")
source("d://MyR//stock//CompareObjectAccuracy.R")

source("d://MyR//zhao//CompareObjectAccuracyArimaNolimitation.R")
source("d://MyR//zhao//ComputeMarketModel.R")
source("d://MyR//zhao//ComputeTMModel.R")
source("d://MyR//zhao//ComputeHMModel.R")
```


```{r 1.2, eval=TRUE}
original.data <- read.csv("d://MyR//zhao//zhao.csv")
# (original.data)
zhao.price <- ts(original.data[,2], start = c(2014, 1), frequency = 12)
money.interest <- ts(original.data[,3], start = c(2014, 1), frequency = 12)
hushen300.price <- ts(original.data[,4], start = c(2014, 1), frequency = 12)
zz500.price <- ts(original.data[,5], start = c(2014, 1), frequency = 12)
zz800.price <- ts(original.data[,6], start = c(2014, 1), frequency = 12)
szhl.price <- ts(original.data[,7], start = c(2014, 1), frequency = 12)
```

```{r 1.3, eval=TRUE}
zhao.monthly.return <- diff(log(zhao.price))
hushen300.monthly.return <- diff(log(hushen300.price))

zz500.monthly.return <- diff(log(zz500.price))

zz800.monthly.return <- diff(log(zz800.price))

szhl.monthly.return <- diff(log(szhl.price))

money.monthly.interest <- ts(log(1 + (money.interest[-1] / 12)),start = c(2014, 2), frequency = 12)

hushen300.monthly.return.no.risk <- ts(round(as.numeric(hushen300.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2014, 2), frequency = 12)


zz500.monthly.return.no.risk <- ts(round(as.numeric(zz500.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2014, 2), frequency = 12)

zz800.monthly.return.no.risk <- ts(round(as.numeric(zz800.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2014, 2), frequency = 12)

szhl.monthly.return.no.risk <- ts(round(as.numeric(szhl.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2014, 2), frequency = 12)

zhao.monthly.return.no.risk <- ts(round(as.numeric((zhao.monthly.return - money.monthly.interest) * 100),
                                     digits = 2),start = c(2014, 2), frequency = 12)
```


```{r 1.4, eval=TRUE}
yearly.return <- diff(log(zhao.price), lag = 12)
two.yearly.return <- diff(log(zhao.price), lag = 24)
```

## 2.  Analysis for monthly return


```{r 2.2, eval=TRUE}
plot(zhao.monthly.return, type = "l")
abline(h = 0, col = "red")
```

```{r 2.3, eval=TRUE}

ndiffs(zhao.monthly.return)

```

```{r 2.4, fig.height=8, fig.width=10}

tsdisplay(zhao.monthly.return)

```



```{r 2.5, eval=TRUE}
mean(zhao.monthly.return)

mean(zhao.monthly.return) * 12

sd(zhao.monthly.return)

sd(zhao.monthly.return) * sqrt(12)

quantile(zhao.monthly.return, c(0.05, seq(0,1,0.25)))

skewness(zhao.monthly.return)
kurtosis(zhao.monthly.return)
jarqueberaTest(zhao.monthly.return)


```

## 3.  Analysis of monthly return for hushen300 with money interest subtracted

```{r 3.0.2, fig.height=8, fig.width=10}
##沪深300求无风险利率期望值
tsdisplay(hushen300.monthly.return.no.risk)
```

```{r 3.0.3, eval=TRUE}

ndiffs(hushen300.monthly.return.no.risk)

```

```{r 3.0.4}

(fit.arima.hushen300.monthly.return <- auto.arima(hushen300.monthly.return.no.risk, 
                                                  stepwise = FALSE, approximation = FALSE))

```

### 3.1 White Noise Test


```{r Monthly Verification--White Noise Test, cache=FALSE, eval=TRUE}

Box.test(residuals(fit.arima.hushen300.monthly.return), 
         lag=round(length(hushen300.monthly.return.no.risk) / 5), 
         fitdf=sum(fit.arima.hushen300.monthly.return$arma[c(1,2)]), type = "Lj")
 
```

### 3.2  Relationship Between Residuals And Time

```{r main 3.2, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.hushen300.monthly.return), axes = TRUE)
abline(h = 0, col = "red")

```

### 3.3 Relationship Between Residuals And Fitted Value

```{r main 3.3, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.hushen300.monthly.return)) ~ as.numeric(fitted(fit.arima.hushen300.monthly.return)))
abline(h = 0, col = "red")


```


### 3.4 Normality of Residuals

```{r Monthly Verification--Normality of Residuals, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.hushen300.monthly.return))
qqline(residuals(fit.arima.hushen300.monthly.return))


```

### 3.5 ARCH Effect Test


```{r Monthly Verification 3.5, eval=TRUE}

Box.test((residuals(fit.arima.hushen300.monthly.return))^2, 
         lag=round(length(hushen300.monthly.return.no.risk) / 5), 
         fitdf=sum(fit.arima.hushen300.monthly.return$arma[c(1,2)]), type = "Lj")

ArchTest(residuals(fit.arima.hushen300.monthly.return))



```

#### 3.6 Comparison of pure Arima model of monthly hushen300 with naive model

```{r appendix 3.6, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}


comparison.period <- 10

forecast.period <- 4

training.set.endpoint <- length(hushen300.monthly.return.no.risk) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 3.6(1), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
result.naive.hushen300 <- CompareObjectNaiveAccuracy(arg.object = hushen300.monthly.return.no.risk,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 3.6(2), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
result.pure.hushen300 <- CompareObjectAccuracy(arg.object = hushen300.monthly.return.no.risk,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 3.6(3), fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure.hushen300$RMSE - result.naive.hushen300$RMSE)

final.result.hushen300 <- cbind(result.pure.hushen300,
                      result.naive.hushen300)


final.result.hushen300 <- final.result.hushen300[, -c(8)]

colnames(final.result.hushen300) <- c("seq", "p","d","q", "dr","RMSE", "p.v",
                            "p2","d2","q2", "dr2","RMSE2", "p.v2")

print(final.result.hushen300)

sum(final.result.hushen300$RMSE > final.result.hushen300$RMSE2)

sum(final.result.hushen300$p.v > 0.05)

sum(final.result.hushen300$p.v2 > 0.05)

```


#### 3.7 Comparison of pure Arima model of monthly hushen300 with another pure model


```{r appendix 3.7(2), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
result.pure.hushen300.no.limitation <- CompareObjectAccuracyArimaNolimitation(arg.object = hushen300.monthly.return.no.risk,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 3.7(3), fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure.hushen300$RMSE - result.pure.hushen300.no.limitation$RMSE)

final.result.hushen300 <- cbind(result.pure.hushen300,
                      result.pure.hushen300.no.limitation)


final.result.hushen300 <- final.result.hushen300[, -c(8)]

colnames(final.result.hushen300) <- c("seq", "p","d","q", "dr","RMSE", "p.v",
                            "p2","d2","q2", "dr2","RMSE2", "p.v2")

print(final.result.hushen300)

sum(final.result.hushen300$RMSE > final.result.hushen300$RMSE2)

sum(final.result.hushen300$p.v > 0.05)

sum(final.result.hushen300$p.v2 > 0.05)

```

### 3.8 Forecast
```{r}
forecast(fit.arima.hushen300.monthly.return, h = 1, 
                              level = c(80,95))
```

```{r}
tail(hushen300.monthly.return.no.risk)
```


## 4.  Analysis of monthly return between zhao and hushen300 with money interest subtracted

### 4.1 Analysis of total data


```{r}
cor(hushen300.monthly.return.no.risk, zhao.monthly.return.no.risk)

fit <- lm(zhao.monthly.return.no.risk ~ hushen300.monthly.return.no.risk)

summary(fit)
```

```{r}
fit.2 <- lm(zhao.monthly.return.no.risk ~ hushen300.monthly.return.no.risk + zz500.monthly.return.no.risk)

summary(fit.2)
```

```{r}
fit.3 <- lm(zhao.monthly.return.no.risk ~ zz800.monthly.return.no.risk)

summary(fit.3)
```

```{r}
fit.4 <- lm(zhao.monthly.return.no.risk ~ zz500.monthly.return.no.risk)

summary(fit.4)
```

```{r}
fit.5 <- lm(zhao.monthly.return.no.risk ~ szhl.monthly.return.no.risk)

summary(fit.5)
```

```{r}
fit.6 <- lm(zhao.monthly.return.no.risk ~ zz500.monthly.return.no.risk + szhl.monthly.return.no.risk)

summary(fit.6)
```

```{r}
fit.7 <- lm(zhao.monthly.return.no.risk ~ hushen300.monthly.return.no.risk  + 
                    szhl.monthly.return.no.risk)

summary(fit.7)
```

```{r}
fit.8 <- lm(zhao.monthly.return.no.risk ~ hushen300.monthly.return.no.risk  + 
                    zz500.monthly.return.no.risk + 
                    szhl.monthly.return.no.risk)

summary(fit.8)
```


```{r, fig.height=6, fig.width=8}
plot(as.numeric(hushen300.monthly.return.no.risk), 
     as.numeric(zhao.monthly.return.no.risk), 
     type = "p", 
     xlab = "沪深300月度超额收益率%", 
     ylab = "赤子之心价值月度超额收益率%", 
     main = "证券特征线")

abline(h = 0, v = 0, col = "green")
points(tail(hushen300.monthly.return.no.risk), tail(zhao.monthly.return.no.risk), col = "purple", pch = 20)

abline(fit)

```


```{r}
## Treynor-Black model
alpha.zhao <- 0.8
sigma.zhao <- 4.5
beta.zhao <- 0.4

return.hushen300 <- 0.4
sigma.hushen300 <- 8

wzhao0 <- (alpha.zhao / (sigma.zhao^2)) / (return.hushen300 / (sigma.hushen300^2))

(wzhao <- wzhao0 / (1 + wzhao0*(1 - beta.zhao)) )



```

### 4.1.1 Analysis of total data using TM model
```{r}
hushen300.monthly.return.square <- hushen300.monthly.return.no.risk^2

fit.tm <- lm(zhao.monthly.return.no.risk ~ hushen300.monthly.return.no.risk + 
                     hushen300.monthly.return.square)

summary(fit.tm)
```

### 4.1.2 Analysis of total data using HM model
```{r}

hushen300.monthly.return.positive <- hushen300.monthly.return.no.risk
hushen300.monthly.return.positive[hushen300.monthly.return.positive < 0] <- 0

fit.hm <- lm(zhao.monthly.return.no.risk ~ hushen300.monthly.return.no.risk + 
                     hushen300.monthly.return.positive)

summary(fit.hm)
```

### 4.2 Analysis of moving 12 months data
```{r}
alpha <- ts(rep(0,length(zhao.monthly.return.no.risk)), start = c(2014, 2), frequency = 12)
beta <- alpha
gamma <- alpha

return.matrix.tm <- cbind(zhao.monthly.return.no.risk, 
                       hushen300.monthly.return.no.risk, 
                       alpha, 
                       beta,
                       gamma) 

dimnames(return.matrix.tm)[[2]][1] <- "zhao"
dimnames(return.matrix.tm)[[2]][2] <- "hushen300"

return.matrix.hm <- return.matrix.tm

return.matrix <- return.matrix.tm[,1:4]
```

```{r}
(return.matrix <- ComputeMarketModel(return.matrix))

```

```{r, fig.height=10, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3), 
                             nr = 3,
                             byrow = TRUE)

layout(plot.layout.matrix)

plot(return.matrix[,"zhao"])
abline(h = 0, col = "green")

plot(return.matrix[,"alpha"])
abline(h = 0, col = "green")

plot(return.matrix[,"beta"])
abline(h = 0, col = "green")

layout(matrix(1))
```

#### 4.2.1 Analysis of moving 12 months data using TM model


```{r}

(return.matrix.tm <- ComputeTMModel(return.matrix.tm))

```

```{r, fig.height=12, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3, 4), 
                             nr = 4,
                             byrow = TRUE)

layout(plot.layout.matrix)

plot(return.matrix.tm[,"zhao"])
abline(h = 0, col = "green")

plot(return.matrix.tm[,"alpha"])
abline(h = 0, col = "green")

plot(return.matrix.tm[,"beta"])
abline(h = 0, col = "green")

plot(return.matrix.tm[,"gamma"])
abline(h = 0, col = "green")

layout(matrix(1))
```

#### 4.2.2 Analysis of moving 12 months data using HM model


```{r}
(return.matrix.hm <- ComputeHMModel(return.matrix.hm))
```

```{r, fig.height=12, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3, 4), 
                             nr = 4,
                             byrow = TRUE)

layout(plot.layout.matrix)

plot(return.matrix.hm[,"zhao"])
abline(h = 0, col = "green")

plot(return.matrix.hm[,"alpha"])
abline(h = 0, col = "green")

plot(return.matrix.hm[,"beta"])
abline(h = 0, col = "green")

plot(return.matrix.hm[,"gamma"])
abline(h = 0, col = "green")

layout(matrix(1))
```

## 5.  Analysis for yearly return

```{r, eval=TRUE}

plot(yearly.return, type = "l")
abline(h = 0, col = "red")
```

```{r, eval=TRUE}

ndiffs(yearly.return)

```

```{r, fig.height=8, fig.width=10}

tsdisplay(yearly.return)

```

```{r, eval=TRUE}
mean(yearly.return)
sd(yearly.return)

quantile(yearly.return, c(0.05, seq(0,1,0.25)))
tail(yearly.return, 2)

skewness(yearly.return)
kurtosis(yearly.return)
jarqueberaTest(yearly.return)


```

## 6.  Analysis of yearly return for portfolio with penghua dollar fund

```{r portfolio with penghua dollar fund, fig.height=8, fig.width=10}
wzhao <- seq(0, 1, by = 0.05)
wpenghua <- 1 - wzhao

##zhao
Erzhao <- 15
sigma.zhao <- 20

##penghua
Erpenghua <- 8
sigma.penghua <- 4

cor.zhao.penghua <- 0.1

# rhuobi <- 5

Ero <- wzhao * Erzhao + wpenghua * Erpenghua

sigmao <- sqrt((wzhao * sigma.zhao)^2 + (wpenghua * sigma.penghua)^2
               +2 * (wzhao * sigma.zhao)*(wpenghua * sigma.penghua) * cor.zhao.penghua)



```

```{r}
rhuobi <- 3.5

Fx1 <- (Erzhao - rhuobi) * sigma.penghua^2 - (Erpenghua - rhuobi) * sigma.zhao * sigma.penghua * cor.zhao.penghua

Fx2 <- (Erzhao - rhuobi) * sigma.penghua^2 + (Erpenghua - rhuobi)*sigma.zhao^2 - 
        (Erzhao - rhuobi + Erpenghua - rhuobi) * sigma.zhao * sigma.penghua * cor.zhao.penghua

(Fzhao <- Fx1 / Fx2)

(Ero.2 <- Fzhao * Erzhao + (1 - Fzhao) * Erpenghua)

(sigmao.2 <- sqrt((Fzhao * sigma.zhao)^2 + ((1-Fzhao) * sigma.penghua)^2
               +2 * (Fzhao * sigma.zhao)*((1 - Fzhao) * sigma.penghua) * cor.zhao.penghua))

(sharpo.2 <- (Ero.2 - rhuobi) / sigmao.2)

(sharpx <- (Erzhao - rhuobi) / sigma.zhao)

(sharpm <- (Erpenghua - rhuobi) / sigma.penghua)


```

```{r}
##try Rdonlp2 package
p <- c(0.5, 0.5)
par.l <- c(0, 0)
par.u <- c(1, 1)

fn <- function(x){
        F1 <- x[1] * Erzhao + x[2] * Erpenghua - rhuobi
        F2 <- sqrt((x[1] * sigma.zhao)^2 + (x[2] * sigma.penghua)^2
               +2 * (x[1] * sigma.zhao)*(x[2] * sigma.penghua) * cor.zhao.penghua)
        F1 / F2
}

A <- matrix(c(1,1), 1, byrow = TRUE)
lin.l <- 1
lin.u <- 1

ret <- donlp2(p, fn, par.u = par.u, par.l = par.l, A, 
              lin.lower = lin.l, 
              lin.upper = lin.u,
              control = donlp2Control(fnscale = -1))

ret$par

ret$fx

ret$message

```


```{r}
plot(sigmao, Ero, 
     xlim = c(0, max(sigmao)),
     ylim = c(0, max(Ero)))

lines(sigmao, Ero)

lines(c(0,sigmao.2), c(rhuobi, Ero.2), col = "blue", lty = "dashed")

```

```{r}
rhuobi <- 4

Fx1 <- (Erzhao - rhuobi) * sigma.penghua^2 - (Erpenghua - rhuobi) * sigma.zhao * sigma.penghua * cor.zhao.penghua

Fx2 <- (Erzhao - rhuobi) * sigma.penghua^2 + (Erpenghua - rhuobi)*sigma.zhao^2 - 
        (Erzhao - rhuobi + Erpenghua - rhuobi) * sigma.zhao * sigma.penghua * cor.zhao.penghua

(Fzhao <- Fx1 / Fx2)

(Ero.2 <- Fzhao * Erzhao + (1 - Fzhao) * Erpenghua)

(sigmao.2 <- sqrt((Fzhao * sigma.zhao)^2 + ((1-Fzhao) * sigma.penghua)^2
               +2 * (Fzhao * sigma.zhao)*((1 - Fzhao) * sigma.penghua) * cor.zhao.penghua))

(sharpo.2 <- (Ero.2 - rhuobi) / sigmao.2)

(sharpx <- (Erzhao - rhuobi) / sigma.zhao)

(sharpm <- (Erpenghua - rhuobi) / sigma.penghua)


```

## 7.  Analysis of yearly return for portfolio with penghua dollar fund and guotai bond fund

```{r}
##zhao
Erzhao <- 15
sigma.zhao <- 20

##penghua
Erpenghua <- 8
sigma.penghua <- 4

##guotai
Erguotai <- 5
sigma.guotai <- 4

cor.zhao.penghua <- 0.1
cor.zhao.guotai <- 0.4
cor.penghua.guotai <- 0.3

rhuobi <- 3.5

##try Rdonlp2 package
p <- c(0.4, 0.4, 0.2)
par.l <- c(0, 0, 0)
par.u <- c(1, 1, 1)

fn <- function(x){
        F1 <- x[1] * Erzhao + x[2] * Erpenghua + x[3] * Erguotai - rhuobi
        
        F2 <- sqrt((x[1] * sigma.zhao)^2 + 
                           (x[2] * sigma.penghua)^2 +
                           (x[3] * sigma.guotai)^2 +
                           2 * (x[1] * sigma.zhao)*(x[2] * sigma.penghua) * cor.zhao.penghua +
                           2 * (x[1] * sigma.zhao)*(x[3] * sigma.guotai) * cor.zhao.guotai +
                           2 * (x[2] * sigma.penghua)*(x[3] * sigma.guotai) * cor.penghua.guotai)
        
        F1 / F2
}

A <- matrix(c(1,1,1), 1, byrow = TRUE)
lin.l <- 1
lin.u <- 1

ret <- donlp2(p, fn, par.u = par.u, par.l = par.l, A, 
              lin.lower = lin.l, 
              lin.upper = lin.u,
              control = donlp2Control(fnscale = -1))

ret$par

ret$fx

ret$message

```

```{r}
fn(c(0.4, 0.4, 0.2))
fn(c(0.2, 0.5, 0.3))
fn(c(0.2, 0.7, 0.1))
fn(c(0.2, 0.8, 0))
```


## 8.  Analysis for 2 years return

```{r, eval=TRUE}

plot(two.yearly.return, type = "l")
abline(h = 0, col = "red")
```

```{r, eval=TRUE}

ndiffs(two.yearly.return)

```

```{r, fig.height=8, fig.width=10}

tsdisplay(two.yearly.return)

```


```{r, eval=TRUE}
mean(two.yearly.return)
sd(two.yearly.return)

quantile(two.yearly.return, c(0.05, seq(0,1,0.25)))
tail(two.yearly.return, 2)

skewness(two.yearly.return)
kurtosis(two.yearly.return)
jarqueberaTest(two.yearly.return)

```


